---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RefineMod

<!-- badges: start -->
```{r, echo = FALSE}                                                                                                        
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])                                                                 
version <- gsub('-', '.', version)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)

<!-- badges: end -->

The goal of RefineMod is to provide functions to refine and optimize linear regression models. Models can be refined to only those predictors that are statistically significant in explaining the response variable. Linear regression models can also be compared on the basis of their performance like RMSE, R2 and MAE.

## Package Development

This package was developed as an assignment for **STAT545B** at UBC using `devtools` and `usethis` packages.

The codes and pipeline used to create this package is as follows

```{r,eval=FALSE}
usethis::create_package(path = "RefineMod") #To initiate the package project locally

usethis::use_git() #To create a git repository of the package locally

```

This local repo is then linked to an empty github repository created with the same name `RefineMod`

```
git remote add origin https://github.com/asfarlathif/RefineMod.git
git branch -M main
git push -u origin main

```
```{r, eval=FALSE}
usethis::use_r("function name") #To create script files of the functions in this package

#All the functions were documented using the roxygen skeleton

devtools::document() #To record the documentation files and update NAMESPACE

usethis::use_readme_rmd() #README file initiation

usethis::use_mit_license() #LICENSE file

usethis::use_code_of_conduct() #CODE OF CONDUCT file

usethis::use_testthat() #To Create tests to include test scripts for the functions
usethis::use_test("function name") #intialize Funstion specific test scripts

usethis::use_package("package name") #To include package dependencies in the DESCRIPTION file

usethis::use_vignette("vignette name") #Initialize vignette RMD file

usethis::use_news_md() #Adding Changelogs

#PACKAGE DIAGNOSIS

devtools::test() #Run all testthat files
devtools::check() #Head to Toe evaluation of the package

```


## Installation

The development version of RefineMod can be installed from [GitHub](https://github.com/) with:

``` r
devtools::install_github("asfarlathif/RefineMod")
```
## Example

### Refining a linear regression model with only its significant predictors

`cancer_sample` data set from `datateachr` package

`radius_mean` as response variable and all (except `diagnosis`) as input predictors

```{r}
library(RefineMod)
library(datateachr)

mod <- lm(radius_mean ~ ., cancer_sample[,-2]) #lm() call without any predictor selection

summary(mod)

```

Above is the model built using all the input predictors as the independent variables while building the model. Many of these variables don’t show any statistical significance (in terms of their p-value) to be included in the model.

```{r}

sig_mod <- lm_significant(cancer_sample[,-2], res = "radius_mean") #model with optimized predictors

summary(sig_mod)

```

`perimeter_mean`, `compactness_mean`, `radius_worst`, `area_worst`, `concavity_mean`, `perimeter_worst` and `compactness_worst` are the predictors that were found to be statistically significant while building a model for the response variable `radius_mean`.

### Comparing Model Performance between one or more lm models

```{r}

train <- mtcars[1:20,]
test <- mtcars[21:30,]

mod1 <- lm(mpg~wt, train)
mod2 <- lm(mpg~cyl, train)
mod3 <- lm(mpg~wt+cyl, train)
mod4 <- lm(mpg~carb, train)

comp_mods(mod1, mod2, mod3, mod4, newdata = test)
```

## Code of Conduct

Please note that the RefineMod project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

