---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RefineMod

<!-- badges: start -->
<!-- badges: end -->

The goal of RefineMod is to provide functions to refine and optimize linear regression models. Models can be refined to only those predictors that are statistically significant in explaining the response variable. Linear regression models can also be compared on the basis of their performance like RMSE, R2 and MAE.


## Installation

The development version of RefineMod can be installed from [GitHub](https://github.com/) with:

``` r
devtools::install_github("asfarlathif/RefineMod")
```
## Example

### Refining a linear regression model with only its significant predictors

`cancer_sample` data set from `datateachr` package

`radius_mean` as response variable and all (except `diagnosis`) as input predictors

```{r}
library(RefineMod)
library(datateachr)

mod <- lm(radius_mean ~ ., cancer_sample[,-2]) #lm() call without any predictor selection

summary(mod)

```

Above is the model built using all the input predictors as the independent variables while building the model. Many of these variables don’t show any statistical significance (in terms of their p-value) to be included in the model.

```{r}

sig_mod <- lm_significant(cancer_sample[,-2], res = "radius_mean") #model with optimized predictors

summary(sig_mod)

```

`perimeter_mean`, `compactness_mean`, `radius_worst`, `area_worst`, `concavity_mean`, `perimeter_worst` and `compactness_worst` are the predictors that were found to be statistically significant while building a model for the response variable `radius_mean`.

### Comparing Model Performance between one or more lm models

```{r}

train <- mtcars[1:20,]
test <- mtcars[21:30,]

mod1 <- lm(mpg~wt, train)
mod2 <- lm(mpg~cyl, train)
mod3 <- lm(mpg~wt+cyl, train)
mod4 <- lm(mpg~carb, train)

comp_mods(mod1, mod2, mod3, mod4, newdata = test)
```

## Code of Conduct

Please note that the RefineMod project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

